Hierarchical Reverberation Mapping

### 2013-08-30 Paper/ms.tex
Fine references

@@

@@

\begin{thebibliography}{99}

>>>>

Recently, \citet{2012MNRAS.427.2701F, 2013MNRAS.434L..16F} introduced an
innovative approach to reverberation mapping where the results from multiple
AGN can be combined to yield inferences about the entire sample of AGN,
despite the fact that the constraints on any individual AGN are poor.

@@

\section{The Inference for a Single Object}
The posterior distribution for the lag of a single object $i$ is obtained
by fitting the following model.

\begin{eqnarray}
blah
\end{eqnarray}

Note that this is already not the cross-correlation.

\section{Demonstration on Simulated Data}

@@

\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Fine et al.}{2013}]{2013MNRAS.434L..16F} 
Fine S., et al., 2013, MNRAS, 434, L16

\bibitem[\protect\citeauthoryear{Fine et al.}{2012}]{2012MNRAS.427.2701F} 
Fine S., et al., 2012, MNRAS, 427, 2701
